Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-23 scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
adding images

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/classroom-maps-axes-annotation.png}
  \caption{The top two images show the Player/Stage classroom simulations used in the example, with the base on the left and the target on the right. The desks are simulated as red boxes, and the chalkboard and lectern (where present) as blue and green boxes respectively. Furthermore, the solid green line in the base connects the boundary points of the front of the room. The lower two images show the metric and place maps generated by Dora during the example runs.}
  \label{fig:dora-maps}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{images/target-success.png}
  \caption{Successful analogical transfer results in the identification of the front of the room as the green dashed trapezoidal region. The red boxes in rows are the identified desks, the blue box along the wall is the chalkboard, the green box is the lectern, and the green and red object is Dora.}
  \label{fig:success}
\end{figure}

>>>>

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{\textbf{TODO}}
  \label{fig:rooms}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/ug40.png}
  \caption{\textbf{TODO}}
  \label{fig:ug40}
\end{figure}

@@

% \begin{figure}[h]
%   \includegraphics[width=\columnwidth]{images/target-success.png}
%   \caption{Successful analogical transfer results in the identification of the front of the room as the green dashed trapezoidal region. The red boxes in rows are the identified desks, the blue box along the wall is the chalkboard, the green box is the lectern, and the green and red object is Dora.}
%   \label{fig:success}
% \end{figure}
